{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-08-01 Notebook LaTEX/Momentum Accelerations/main.tex
>w< work, home sync

                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2

@@

                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2

@@

            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]

@@

                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2

@@

                \right) := \Upsilon_{1, t + 1}^\text{AG}

>>>>

                    % + 
                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2

@@

                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
                    % + 

@@

            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ if we ignore the difference between the constant terms $h(y_t^+)$, $f(y_t) + g(y_t)$ from above. 
            Therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]

@@

                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
                    % + 

@@

                \right) =: \Upsilon_{1, t + 1}^\text{AG}
